Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-06-14 paper/ms.tex
done with the major points

@@

\bibliographystyle{apj}
%\bibliography{references.bib}
\begin{thebibliography}{39}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

@@

>>>>

We do not include the covariance matrix due to the
practical impossibility to estimate it in a robust way.
The small size of the fields and galaxies make it
unfeasible the application of jackknife and bootstrap techniques \citep{2009MNRAS.396...19N}. 
An estimate from N-body simulation faces the same problem with the
additional limitation that we want to solve in the first place. 
Namely, not knowing the range of halo masses that produces the
observed clustering signal.  
Tests that we performed in the simulation show that, due to the small
number of points to estimate the clustering, the covariance matrix is
not stable, even for similar models. 
Using the full error covariance matrix, when not noise
dominated, versus only diagonal elements usually has a small effect
on clustering analyses \citep{2011ApJ...736...59Z}.

@@

\bibliographystyle{apj}
%\bibliography{references.bib}

\begin{thebibliography}{39}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

\bibitem[{{Norberg} {et~al.}(2009){Norberg}, {Baugh}, {Gazta{\~n}aga}, \&
  {Croton}}]{2009MNRAS.396...19N}
{Norberg}, P., {Baugh}, C.~M., {Gazta{\~n}aga}, E., \& {Croton}, D.~J. 2009,
  \mnras, 396, 19

@@

\bibitem[{{Zehavi} {et~al.}(2011){Zehavi}, {Zheng}, {Weinberg}, {Blanton},
  {Bahcall}, {Berlind}, {Brinkmann}, {Frieman}, {Gunn}, {Lupton}, {Nichol},
  {Percival}, {Schneider}, {Skibba}, {Strauss}, {Tegmark}, \&
  {York}}]{2011ApJ...736...59Z}
{Zehavi}, I., {Zheng}, Z., {Weinberg}, D.~H., {Blanton}, M.~R., {Bahcall},
  N.~A., {Berlind}, A.~A., {Brinkmann}, J., {Frieman}, J.~A., {Gunn}, J.~E.,
  {Lupton}, R.~H., {Nichol}, R.~C., {Percival}, W.~J., {Schneider}, D.~P.,
  {Skibba}, R.~A., {Strauss}, M.~A., {Tegmark}, M., \& {York}, D.~G. 2011,
  \apj, 736, 59
